Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
background edits

In any quantum computing processes, the building blocks of the process are qubits. A qubit, or quantum bit, is the quantum analogue of the classical
 bit (strings of zeros and ones). So the qubit represents a quantum superposition or combination of a predetermined ‘0’ and a ‘1’ state. The quantum
  algorithms were run on superconducting qubits, these are a physical realisation of quantum bits based upon what are known as superconducting
  interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule (in this case molecular Hydrogen).

>>>>

The building blocks of any quantum computing process may be considered to be qubits. A qubit, or quantum bit, is the quantum analogue of the
classical bit in which classical information is encoded in 0s and 1s. So the qubit represents a quantum superposition or simultaneous combination of
both a predetermined ‘0’ and a ‘1’ state. The quantum algorithms were run on superconducting qubits, these are a physical realisation of quantum bits
 based upon what are known as superconducting interference devices (SQUIDs), and attempt to find properties of the wavefunction of the molecule
 (in this case molecular Hydrogen).
